---
title: "Churn Analysis-Telco data"
author: "Wei-Ting,Lin"
date: "7/15/2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


#### Churn Analysis using Logistic Regression with Telco data

> Goal : predict behavior to retain customers

The data set includes information about:

* Customers who left within the last month – the column is called Churn
* Services that each customer has signed up for – phone, multiple lines, internet, online security, online backup, device protection, tech support, and streaming TV and movies
* Customer account information – how long they’ve been a customer, contract, payment method, paperless billing, monthly charges, and total charges
* Demographic info about customers – gender, age range, and if they have partners and dependents


data source <https://www.kaggle.com/blastchar/telco-customer-churn>


```{r}
library(readr)
library(dplyr)
library(ggplot2)
library(MASS)
library(boot)
library(caret)
library(e1071)
```


```{r}
#import data (default stringAsFactor = TRUE )
customer <- read.csv("~/Onedrive/R_coding/test_git/WA_Fn-UseC_-Telco-Customer-Churn.csv")
View(customer)
 
```

### Data wrangling 
```{r}
# Make ID back to correct format
customer$customerID <- as.character(customer$customerID)

#reorder
customer <- customer[c(1,21,2:20)]

# scan missing value
colSums(is.na(customer))

#observation with missing values 
missing <- filter(customer, is.na(customer$TotalCharges) == TRUE )

# since TotalCharges is roughly equals to tenure * monthly charges, I replace the missing value accordingly.
customer_m <- customer %>% mutate(TotalCharges = ifelse(is.na(customer$TotalCharges), customer$MonthlyCharges*customer$tenure, TotalCharges) )

```


#### check for outliers
```{r}

boxplot(customer_m$tenure)

boxplot(customer_m$MonthlyCharges)
# not outliers 
```


### Exploring data 
#### How many churns in this dataset ? 
```{r}
ggplot(customer_m, aes(x = Churn))+
  geom_histogram(stat = "count", fill = c("sky blue", "orange"))
  
# churn yes : 1869 , no: 5174
```


#### When do customer churns ? 
```{r}
# churn mostly happens in short tenure
customer_m %>% filter(customer_m$Churn == "Yes") %>% 
  ggplot( aes(x=  tenure))+
  geom_bar(fill = "orange" )
```


#### Model Specification
```{r}

# full logistic model 

logisticModelFull <- glm(Churn ~  gender + SeniorCitizen + Partner + Dependents + tenure + PhoneService + MultipleLines + InternetService + OnlineSecurity + OnlineBackup + DeviceProtection + TechSupport + StreamingTV + StreamingMovies + Contract + PaperlessBilling + PaymentMethod + MonthlyCharges , family = "binomial", customer_m)

summary(logisticModelFull)
```

#### new model (optimize model by finding the min. AIC value)

```{r}

logisticModelNew <-  stepAIC(logisticModelFull, trace = 0)

summary(logisticModelNew)
```


#### Interpretation of coefficient 
interpretation of odds : eg.  user with  Multiple Lines (MultipleLinesYes) increase the odd of churn by 35%. Being a senior citizen is 24% more likely to churn than non-senior citizen group. 
```{r}
# transform Coefficient to Odds

odds <-  coef(logisticModelNew) %>% exp() %>% round(2)

odds

```


***

### Out-of-sample validation and cross validation

#### devide data into training & testing set
* Training set : 2/3 of data 
* Testing set : 1/3 of data
```{r}
#generating random index for training & testing set
set.seed(2345)

customer_m$isTrain <- rbinom(nrow(customer_m),1,0.66)

train <-  customer_m %>% filter(customer_m$isTrain =="1")
test <- customer_m %>%  filter(customer_m$isTrain == "0")
```



#### train model 

```{r}
# modeling 
LogisticTrainNew <- glm( Churn ~ gender + SeniorCitizen + Partner + Dependents + tenure + PhoneService + MultipleLines + InternetService + OnlineSecurity + OnlineBackup + DeviceProtection + TechSupport + StreamingTV + StreamingMovies + Contract + PaperlessBilling + PaymentMethod + MonthlyCharges , family = "binomial", train)

#prediciton 
test$predictNew <- predict(LogisticTrainNew , type = "response" , newdata = test)


#confusion matrix & accuracy 
confMatrix <- confusion.matrix(test$Churn, test$predictNew, threshold = 0.5) 

```



